---
title: "HW-02: Shot Charts"
author: "Phoebe Abramowitz"
date: "3/4/2018"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, fig.path='../images')
```
## Question 5.1
```{r}
library("dplyr")
library('ggplot2')

shots_data <- read.csv('../data/shots-data.csv')


#group by player name and count number of shots 
player_shot_count<- count(shots_data, name, sort=TRUE)
psc <- rename(player_shot_count,total=n)
psc
```
## Question 5.2
```{r}
#effective shooting percent by player
efctv_shot_count<- rename(count(filter(shots_data, shot_made_flag=="made shot"), 
                                name), made=n)
comb <- left_join(psc,efctv_shot_count)
shooting_perc <- arrange(mutate(comb, perc_made=(made/total)),desc(perc_made))



shots_data_2pt <- filter(shots_data, shot_type=="2PT Field Goal")
psc_2pt <- rename(count(shots_data_2pt,name, sort=TRUE),total=n)

efctv_shot_count_2pt<- rename(count(filter(shots_data_2pt, shot_made_flag=="made shot"),
                                    name), made=n)
comb_2pt <- left_join(psc_2pt,efctv_shot_count_2pt)
shooting_perc_2pt <- arrange(mutate(comb_2pt, perc_made=(made/total)),desc(perc_made))


shots_data_3pt <- filter(shots_data, shot_type=="3PT Field Goal")
psc_3pt <- rename(count(shots_data_3pt,name, sort=TRUE),total=n)

efctv_shot_count_3pt<- rename(count(filter(shots_data_3pt, shot_made_flag=="made shot"),
                                    name), made=n)
comb_3pt <- left_join(psc_3pt,efctv_shot_count_3pt)
shooting_perc_3pt <- arrange(mutate(comb_3pt, perc_made=(made/total)),desc(perc_made))


shooting_perc_2pt
shooting_perc_3pt
shooting_perc
```
## Question 6
```{r}

shots_data_dist <-mutate(shots_data,shot_distance=round(sqrt(x^2+y^2)))

                        
dist_shot_count <- count(shots_data_dist, shot_distance)

dsc <- arrange(rename(dist_shot_count,total=n),shot_distance)
dsc

efctv_shot_dist<-count(filter(shots_data_dist, shot_made_flag=="made shot"),
                                shot_distance)
efctv_shot_dist

comb_dist <- left_join(dsc,efctv_shot_dist)
comb_dist
shooting_perc_dist <- arrange(mutate(comb_dist, 
                                     made_shot_prop=(n/total)))
spd <- select(shooting_perc_dist,shot_distance,made_shot_prop)
spd
```
## Question 6.2
```{r}
ggplot(data=slice(spd,1:38))+
  geom_point(aes(x=shot_distance,y=made_shot_prop),color="blue")+
  ggtitle("Proportion of shots made by distance, up to 38in from net")
ggplot(data=spd)+
  geom_point(aes(x=shot_distance,y=made_shot_prop),color="green")+
  ggtitle("Proportion of shots made by distance")
```
###Observations:/
Looking at the overall scatter plot, there's not an obvious overall downward trend, so we can't confirm that the shorter/ the distance, the more effective the shots. There is however, a clearly visible downward trend within 38 inches of the net./
It's worth noting that there's much higher rates of shooting very close to the net and around 230 inches(closest to the net/ while in the 3-point zone), so there's many more baskets made from there despite scattered proportions. Very few shots are/ taken more than 300 inches from the net. The 20 inches closest to the net all have a >50% of making the shot. I can't infer/
the distance at which chances of making a shot are basically null, but almost no shots are taken beyond 300 inches/ away.
If players are choosing not to take shots further than that, it's probably because they don't beleive they/ can be effective.\

## Question 7

```{r}
d <- data.frame(x1=c(0,24),y1=c(0,0),x2=c(12,36),y2=c(60,60))

by_minute_player <-count(shots_data,minute,name)
gsw_shot_chart <- ggplot(data=by_minute_player)+
  geom_rect(data=d,mapping=aes(xmin=x1,ymin=y1,xmax=x2,ymax=y2),fill="grey97",color="grey90")+
  geom_path(aes(x=minute,y=n),color="lightblue2")+
  geom_point(aes(x=minute,y=n),color="steelblue2",shape=20)+
  ylim(0,60)+
  facet_wrap(~name)+
  scale_x_continuous()+
  ggtitle("Total Number of Shots(By Minute of Occurence)")+
  theme_minimal()+
  labs(x="minute",y="total number of shots")

gsw_shot_chart
```

